Tail associations and their impact on extinction risk

### 2019-11-09 MainText.Rmd
added 'mathematical ecology' as a keywrd

csl: TheAmericanNaturalist.csl
bibliography: Ref_extrisk.bib
---

@@

\vspace{12pt}
\noindent \textbf{\textit{Keywords:}} extinction risk, extreme events, tail association, density-dependent model, copula

>>>>

csl: ecosphere.csl
bibliography: Ref_extrisk.bib
---

@@

\vspace{12pt}
\noindent \textbf{\textit{Keywords:}} extinction risk, extreme events, tail association, density-dependent model, copula, mathematical ecology
